---
title: "Activity 2 - Day 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
```


```{r getdata}
hfi <- readr::read_csv("https://www.openintro.org/data/csv/hfi.csv")
```

```{r filter}
hfi_2016 <- filter(hfi, year == 2016)
```

```{r plot}
# plot(hfi_2016$pf_expression_control, hfi_2016$pf_score)
statsr::plot_ss(x = pf_expression_control, y = pf_score, data = hfi_2016, showSquares = TRUE)
```


```{r linear model}
m1 <- lm(pf_score ~ pf_expression_control, data = hfi_2016)
tidy(m1)
```

## Day 2
### Overall model fit
```{r dplry}
hfi_2016 %>%
  summarize(cor=cor(pf_score,pf_expression_control))
```

There is a strong positive correlation between `pf_score` and `pf_expression_control`.

```{r rsquared}
glance(m1)
```

The r-squared value for this model is `.71`, which means that this model is `71%` more accurate than using the mean `pf_score` of the dataset as our predictor.

### Create a New Model
```{r hf-model}
m2 <- lm(hf_score ~ pf_expression_control, data = hfi_2016)
tidy(m2)
```
Countries have a base mean hf_score of `5.053` and for every unit of `pf_expression_control`, `hf_score` will increase by `0.368`.

### Prediction and prediction errors
```{r plot task 3}
hfi_2016 %>% 
  ggplot(aes(x=pf_expression_control, y=pf_score)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_point() + 
  theme_bw() + 
  ggtitle('pf_score vs. pf_expression_control')
```

### Model Diagnostics
```{r augment}
m1_aug <- augment(m1)
```

```{r residual chart}
ggplot(data = m1_aug, aes(x = .fitted, y = .resid)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  xlab("Fitted values") +
  ylab("Residuals") + 
  theme_bw()
```
The residuals look like they have constant variance until the higher predicted values where variance seems to decrease.

```{r histogram}
ggplot(data = m1_aug, aes(x = .resid)) +
  geom_histogram(binwidth = 0.25) +
  xlab("Residuals") + 
  theme_bw()
```
Constant variability appears to be violated because the historgram is not a normal curve, having a left skew.

### Challange: More Practice

```{r another variable}
hfi_2016 %>%
  ggplot(aes(x = pf_expression_influence, y = pf_score)) +
  geom_point()
  
m3 <- lm(pf_score ~ pf_expression_influence, data = hfi_2016)
tidy(m3)

glance(m3)
```

